\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-07 doc/sw-system.tex
Fixed #165

Most of the text of the Spotter's Guide focuses on the kinds of features that
gravitational lenses do or don't produce. To complement this,
the website ``Science page'' contains a very brief introduction to how
gravitational lensing works, which is fleshed out a little on the ``FAQ'' page.
The FAQ also contains answers to frequently asked questions about the interface
and the task set.

>>>>

Most of the text of the Spotter's Guide focuses on the kinds of features that
gravitational lenses do or don't produce. To complement this,
the website ``Science'' section contains a very brief introduction to how
gravitational lensing works, which is fleshed out a little on the ``FAQ'' page.
The FAQ also contains answers to questions about the interface
and the task set.
